To analyze and extend the applicability of openISBT, we construct an experiment. Figure \ref{fig:structure_of_the_experiment} shows the experiment design. In this experiment, we first collect a set of OpenAPI documents from SwaggerHub. Next, we use an evaluation tool to determine the applicability of openISBT.
Afterward, we derive new abstract operations and extend openISBT. Therefore, we analyze all service operations that openISBT cannot match, cluster them into groups of operations with similar purposes, and analyze common properties for each group.  We design and implement new matching units to match service operations to the new abstract operations based on these common properties. Finally, we repeat the measurement and compare the results of both measurements.


Computer programs automate both the data collection process and the measurements described above. Therefore, we require preceding activities that the experiment design in figure \ref{fig:structure_of_the_experiment} does not reveal. We design and implement a web crawler to collect OpenAPI documents and a tool that executes the measurements. The tool also integrates the components for data cleaning. Chapter \ref{cha:collecting_oas_files} presents the web crawler's design and implementation and several components for data cleaning. Chapter \ref{cha:analyzing_oas_files} discusses aspects regarding the measurement design and measurement execution. It presents the evaluation tool's design and architecture and discusses the first measurement results. 
Chapter \ref{cha:extending_openisbt} discusses data findings, presents new abstract operations and contributions to openISBT.
Finally, chapter \ref{cha:evaluating_new_abstact_operations} presents the results of the second measurement. It compares both measurements' results and highlights the achieved improvement.

