
\begin{longtable}{ m{3cm} | m{11.5cm}}
\caption{Modules and their tasks} 
\label{tab:derived_tasks} \\

\multicolumn{1}{c}{\textbf{Category}} & 
\multicolumn{1}{c}{\textbf{Tasks}} \\

\toprule
\endfirsthead

\multicolumn{2}{c}%
{\tablename\ \thetable{} -- continued from previous page} \\ 
\multicolumn{1}{c}{\textbf{Category}} &
\multicolumn{1}{c}{\textbf{Tasks}}
\\
\toprule
\endhead

\midrule
\multicolumn{2}{r}{{Continued on next page}} \\
\endfoot

\bottomrule
\endlastfoot
Pre-Binding-Tasks &
Before our tool can do the binding there are several cleaning and transforming steps to be done. 
\begin{itemize}
    \item \textbf {Discard non-production OAS files:} As we want to analyse only APIs used in production we have to remove all other APIs before doing our analysis , what as a matter of fact would result in a manual research and investigation for each file. As this seems to be infeasible for large sets we needed find criteria to implement automated discarding to at least reduce non-production data. We made a hard assumption that short OAS file is probably not used in production. This approach results in a trade-off as we on the one hand might discard small APIs used in production but on the other hand might miss out non-production APIs. Nonetheless, we decided that reducing our    
    \item read the files and save a file summary in a file
    \item remove unreadable files
\end{itemize} 
\\
\hline
Binding &
\begin{itemize}
    \item bind log the files, catch error and associate errors to files
\end{itemize} 
\\
\hline
Post-Binding-Tasks &
\begin{itemize}
    \item remove files that caused errors from the set of files we want to evaluates
    \item remove sample files. This could also be done in the pre-binding-phase but it's way easier to do it in the post-binding-phase.
\end{itemize} 
\\
\hline
Main analysis &
\begin{itemize}
    \item coverage criteria1: analyse the log files analyse the api. log result of both and do the maths
    \item coverage criteria2 analyse the log files analyse the api. log result of both and do the maths
\end{itemize}
\\ 
\hline
Additional Analysis & 
\begin{itemize}
    \item count operations in file that threw exception 
    \item count operations in files that only define subresources
\end{itemize} 
\\
\end{longtable}