This chapter covers aspects of the second measurement execution for the extended openISBT version. It presents the results and compares them to the results of the previous measurement. 

\input{mainmatter/07_evaluating_new_patterns/07_content/02_1_pie chart_coverage_criteria_main}

We use an extended pattern configuration file for the measurement execution, which defines four new interaction patterns, each containing one new abstract operation. 
Appendix \ref{app:results_data_cleaning2} shows that nine more OpenAPI documents cause exceptions in openISBT because of code changes.
Therefore, we determine metrics for a smaller sample and can only compare relative values. 

\input{mainmatter/07_evaluating_new_patterns/07_content/02_2_pie_chart_operation_types}

The following metrics belong to a set of 1172 OpenAPI documents, which define 13233 service operations. Figure \ref{fig:analysis2_pie_both_criteria_main} shows two pie charts, which visualize the coverage metrics $p_{operations}$ and $p_{APIs}$. Figure \ref{fig:analysis2_sub_pie_coverage_sup_operations_main} shows that the extended openISBT version can match 10897 (82.3\%) service operations. Therefore, the coverage $p_{operations}$ is 7.1\% higher than in the first measurement execution (see figure \ref{fig:analysis1_sub_pie_coverage_sup_operations_main}).Figure \ref{fig:analysis2_sub_pie_coverage_full_sup_apis_main} shows that the extended openISBT version can match any operation in 572 (48.8\%) OpenAPI documents. 
Comparing it to figure \ref{fig:analysis1_sub_pie_coverage_full_sup_apis_main}, we notice an increase of $p_{APIs}$ of 7.4\%.

Figure \ref{fig:analysis2:pie_chart_shares_of_operation_types} shows the distribution of abstract operations as a pie chart. 
Comparing it to the prior distribution in figure \ref{fig:analysis1:pie_chart_shares_of_operation_types}, we see that each value changed. However, for the abstract operations CREATE, UPDATE, and DELETE, the change is minimal and subject to the changed sample size.
The decrease in the coverage of undefined operation is $\Delta p_{operations}$.
There are representants for all new abstract operations in the sample.
We see an increase in the coverage of the SCAN operation from 9.29\% to 10.32\%. 
The coverage of the READ operation shows a decrease from 13.97\%  to 10.44\%. As the modifications to the matching units we describe in section \ref{sec:extending:improving_existing_matching_units} are not restrictive, we assume a shift from the READ operation to other abstract operations. 